\documentclass{letter}

\usepackage{censor}

\title{}
\author{\protect\censor{AAAAAAAAAAAAAA}| \protect\censor{AAAAAAAAAAAA}| \protect\censor{AAAAAAAAAAA}| \protect\censor{AAAAAAAAAAAA}}
\to{Dr.Teslenko}
\position{MECH226 Instructor| University of British Columbia|2329 West Mall, Vancouver, BC}
\date{December 6, 2017}

\begin{document}

\maketitle

The following is our formal report about human computer interactions in the workplace for  MECH 226, technical communication. 

In our report, \emph{Ethics of Artificial Intelligence in the North-American Workplace}, we look at the issues regarding the creation of AI systems, their problematic subjectivity, their accountability, and future guidelines required for their use. 
Since AI appears in many instances, we have not restricted the report to any workplace in particular.

Ethical issues first arise when considering AI’s operating system and the limited understanding and trust society has with its methods. 

The second ethical issue covered in the report is the inherent biases in AI and their impact in the workplace. 
The report also covers the various methods of attributing accountability for AI mishaps. 
Finally, the report looks at the future guidelines and judicial structures that should be created by major organizations for safe future use of AI. 

The report outline has been reorganised from the proposal to allow better flow between the three ethical issues and the final section on addressing those issues. 
This new order allows the issues to be organized chronologically: from configuration, to usage, to impact, to regulation of AI. 
Also, as noted in a previous meeting, the “Allocation of Accountability” section does not require a figure. 

The creation of this report has better educated our group on AI’s moral considerations. 

Writing this report has broadened our understanding on AI. 
Thank you for dedicating your time to read our report, and we will gladly answer any questions you may have. 
This can be accomplished by contacting our team lead, \censor{AAAAAAAAAAAA}, through email at \censor{AAAAAAAAAAAAAAAAAAAAAAA} anytime. 

\makeend

\end{document}
