%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Memo
% LaTeX Template
% Version 1.0 (30/12/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rob Oakes (http://www.oak-tree.us) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper,11pt]{memo} % Set the paper size (letterpaper, a4paper, etc) and font size (10pt, 11pt or 12pt)
\usepackage{censor}

\usepackage{parskip} % Adds spacing between paragraphs

%----------------------------------------------------------------------------------------
%	MEMO INFORMATION
%----------------------------------------------------------------------------------------

\memoto{Professor Teslenko, MECH 226 Instructor} % Recipient(s)

\memofrom{\protect\censor{AAAAAAAAAAAAAA}, \protect\censor{AAAAAAAAAAAA}, \protect\censor{AAAAAAAAAAA}, \protect\censor{AAAAAAAAAAAA}} % Sender(s)

\memodate{\today} % Date, set to \today for automatically printing todays date

\memosubject{Ethical Concerns of Artificial Intelligence Involvement in the North-American Workplace} % Memo subject

%----------------------------------------------------------------------------------------


\begin{document}
\pagenumbering{gobble}
\maketitle % Print the memo header information

%----------------------------------------------------------------------------------------
%	MEMO CONTENT
%----------------------------------------------------------------------------------------
In response to your request for a report about ethical issues pertaining to human-computer interaction we seek your approval for our report. % Reword this sentence
This memorandum outlines our proposed report about the ethical concerns of the societal impact of artificial intelligence (AI).
It describes the purpose, significance, and audience of the report in addition to its scope, methods, team qualifications, and allocation of roles between team members. 

\section{Topic and Background}
The rising presence of artificial intelligence in the workplace raises ethical concerns. 
Traditional communication is altered by the fact that more and more communicators are no longer consist of  human beings. 
This presents both potential benefits and detriments to society. 
They should be taken into consideration when deciding the point to which we integrate AI in the workplace. 

\section{Purpose}
The purpose of this report is to  examine the impact of AI in the workplace.  
It will focus on the ethics associated with AI involvement as opposed to a human interaction.
We will focus on the risks associated with accountability, transparency, and bias.
We will also consider the concerns with future guidelines for AI usage in  the future. 

\section{Significance}
In recent years, AI technologies have become incredibly powerful. 
Because of this, many companies are looking to integrate this technology into their work-flows. 
However, AI is far from being ready to completely automate all positions. 
These systems must be designed to communicate with humans in an easily understandable and ethical manner.
\pagebreak

\section{Audience}
The report is intended for an educated layperson familiar with the basic concepts of an AI system. 
Our primary audience is Professor Teslenko, the MECH 226 instructor, and  Amin Mahmud, the MECH 226 teaching assistant, who will be reading and marking the paper. 
The secondary audience is the rest of the MECH 226 class which will edit and read the paper, and future MECH 226 students as a sample resource.


\pagenumbering{arabic}
\setcounter{page}{2}

\section{Scope}
To assess the ethical implications of integrating AI powered human computer interfaces into society, we plan to discuss the following topics: 
\begin{enumerate}
	\item Who is accountable for the actions/recommendations of an AI system?
	\item Which implicit biases are present in AI?
	\item Can we make AI more transparent?
	\item What type of guidelines must be established to make AI usage more ethical?
\end{enumerate}

\section{Methods}
We will use the following methods to complete the report:
\begin{enumerate}
	\item Communication: 
	The completion of our project is coordinated through group communication in a private messaging group. 
	We have, and plan to continue, meeting weekly in the Engineering Student Center when our shared schedule permits. 
	\censor{AAAA}, our selected team leader, is in charge of organizing meetings.
	\item Assign roles: 
	As detailed in the enclosed project planning form, we have allocated various tasks based on individual strengths. 
	This allows us to address unique aspects of the report to the best of our ability. 
	\item Research: 
	We have acquired peer-reviewed scholarly articles as secondary sources about our topic using the UBC library access to online databases. 
	We will find sources for the sections of the report as well as general articles about AI.
	\item Composition: 
	We will collaboratively write our documents in Git and use Google Docs as an auxiliary to share meeting notes and rough outlines. 
\end{enumerate}

\pagebreak
\section{Team Qualifications}
Group 1 consists of four second-year mechanical engineering students: \protect\censor{AAAAAAAAAAAAAA}, \protect\censor{AAAAAAAAAAAA}, \protect\censor{AAAAAAAAAAA}, and \protect\censor{AAAAAAAAAAAA}. 
Our unique experiences and backgrounds have allowed us to garner distinct skills suited to specific roles involved in writing a piece of technical communication. 
Here is a list of our individual strong-suits: 
\begin{itemize}
	\item \censor{AAAAAA} has experience in writing design project reports as well as reporting work progress in an NGO.
	\item \censor{AAAAAA} has served as team captain  and editor in both of her first year design projects. 
	She is prolific in two languages and has received academic recognition in English. 
	\item \censor{AAAAAA} has written multiple research papers and is proficient in \LaTeX \space and Git.
	\item \censor{AAAA} has coached soccer, directed theater, and lead multiple team team projects in university. 
\end{itemize}

\section{Conclusion}
We have enclosed a project planning form, a preliminary report outline, a proposed list of figures, and an annotated bibliography.
The final report will follow the proposed outline, although it may include minor changes if required. 
We would appreciate any feedback about our proposed outline and topic. 
Your word of approval is crucial for the advancement of our final report. 
Any questions or concerns that may arise can be directed to our team leader. 
To contact us, please email \censor{AAAAAAAAAAAA} at \censor{AAAAAAAAAAAAAAAAAAAAAAA}. 
Thank you for your time and consideration.

\vspace{5mm}

\listofenclosure

\pagebreak

\enclosure{Project Planning Form}{../bin/proposal.pdf}
\enclosure{Gantt Chart}{../bin/gantt.pdf}
\enclosure{Tentative Report outline}{../bin/outline.pdf}
\enclosure{Annotated Bibliography}{../bin/bib.pdf}
\enclosure{Proposed List of Illustrations}{../bin/illustrations.pdf}

\pagenumbering{gobble}
\phantom x



%----------------------------------------------------------------------------------------

\end{document}